---
title       : Coursera Slidify Assignment
subtitle    : 
author      : Serge Kestens (IOTConsult)
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz, shiny, interactive]
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction
<br>
<br>
<br>
<br>

For this assignment, we need to create 5 slides in Slidify.<br>
The first slides contain a small description and introduction.<br>
Slide 3 will do the needed calculations on the dataframe.<br>
Slide 4 presents these results in a GoogleVis Line Chart.<br>
Slide 5 presents the same results in a GoogleVis Table.<br>


--- .class #id 
## Data calculations on an imported rds file

```{r,echo=TRUE}
setwd ("C:/Users/gjf510/Google Drive/DataScience/Projects/coursera/devdata/IOTConsult")
TotalRevenue <- readRDS("data/TotalRevenue.rds")
#print(TotalRevenue)
library(plyr)
library(reshape2)

Revenue <- ddply(TotalRevenue, c("Year"), summarise,
                Total = sum(Total),
                Services = sum(Services),
                Products = sum(Products))
print(Revenue)
```

--- &interactive
## GoogleVis Linechart example
<br>
<br>
```{r results='asis',echo=FALSE}
suppressPackageStartupMessages(require(googleVis))
Line <- gvisLineChart(Revenue,xvar="Year",yvar=c("Total","Services","Products"),
                      options=list(width=900, height=300, 
                                     legend='bottom',
                                     hAxis="{title:'Type'}",
                                     vAxis="{title:'Total'}")
                      )
print(Line, 'chart')
```

---
## GoogleVis Table example
<br>
<br>
```{r results='asis',echo=FALSE}
require(googleVis)
Table <- gvisTable(Revenue, 
                    formats=list(Products="#,###",Services="#,###",Total="#,###"),
                    options=list(page='enable')
                   )
print(Table, 'chart')
```





